---
title: "About"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

The American cranberry (*Vaccinium macrocarpon* Ait.) is native to eastern North America, yet plant explorations and collections have sampled only a narrow subset of the native range. Our goal is to expand the scope of cranberry material collected from native stands such that the diversity of environments in the native range is sufficiently sampled.


## Occurrence Information

Cranberry occurrence observations were obtained from iNaturalist and GBIF. We also collating passport information for accessions of cranberry held in the USDA National Clonal Germplasm Repository in Corvallis, OR and listed on GRIN. An interactive map of that data is below.


```{r plot}

## Plot cranberry occurrence data
##

library(tidyverse)
library(readxl)
library(neyhart)
library(plotly)

fig_dir <- "output"


# Read in data ------------------------------------------------------------

dat <- read_excel(path = "data/cranberry_occurrence_data.xlsx")




# Plot --------------------------------------------------------------------

xlim <- c(min(dat$longitude, na.rm = TRUE), -55)
ylim <- range(dat$latitude, na.rm = TRUE)

# Colors for source
# source_colors <- setNames(umn_palette(3)[3:5], unique(dat$source))
# source_colors <- setNames(umn_palette(2)[3:5], unique(dat$source))
# source_colors <- setNames(neyhart_palette("barley")[1:3], unique(dat$source))
source_colors <- setNames(neyhart_palette("barley")[1:3], c("GRIN", "iNaturalist", "GBIF"))


# Create a base map
g_base_map <- ggplot(data = north_america_mapdata, aes(x = long, y = lat)) +
  geom_polygon(fill = "white") +
  geom_polygon(data = subset(north_america_mapdata, area == "canada"),
               aes(group = group), fill = "grey95", color = "grey50", linewidth = 0.5) + # Add canada
  geom_polygon(data = subset(north_america_mapdata, area == "usa_state"),
               aes(group = group), fill = "grey95", color = "grey50", linewidth = 0.5) +  # Add location points
  coord_map(projection = "bonne", lat0 = mean(ylim), xlim = xlim, ylim = ylim) +
  scale_color_manual(values = source_colors) +
  theme_void(base_size = 14) +
  theme(legend.position = "top", legend.box = "vertical", legend.box.just = "left")

# Add points
g_cran_points <- g_base_map +
  geom_point(data = dat, aes(x = longitude, y = latitude, color = source, shape = source))

# Different size points
g_cran_points1 <- g_base_map +
  geom_point(data = subset(dat, source != "GRIN"), size = 0.75,
             aes(x = longitude, y = latitude, color = source)) +
  geom_point(data = subset(dat, source == "GRIN"), size = 2,
             aes(x = longitude, y = latitude, color = source))

ggplotly(g_cran_points1)

```
